---
title: "Session 1 lab: Association between cholesterol and age"
author: "Levi Waldron"
institute: "CUNY SPH Biostatistics 2"
output:
  html_document:
    toc: yes
    df_print: paged
    theme: lumen
    number_sections: yes
---

**Learning objectives**

1. Load a tab-separated dataset into R
2. Create a simple scatterplot using `ggplot2`
3. Fit and analyze a multiple linear regression model
4. Compare two nested models using a nested Analysis of Variance (partial F test)

**Exercises**

1. Load the `cholesterol.tsv` dataset into R
2. Fit linear models with age, state, and interaction terms as predictors
3. Compare a simple linear regression to a multiple linear regression using Analysis of Variance partial F-test
4. Use backwards selection from a full model with interactions to choose the best prediction model

# Load the dataset

Figure out this command using `File - Import Dataset`

```{r}
library(readr)
chol <- read_table("cholesterol.tsv", 
    col_types = cols(age = col_double()))
summary(chol)
```

# Create a scatterplot of  Cholesterol vs. Age

Take Data Science Module 1 "Data Visualization Basics" first if you aren't familiar with `ggplot2`:
```{r, message=FALSE}
library(ggplot2)
ggplot(chol, aes(x=age, y=cholesterol, shape=state, color=state)) + 
  geom_point(size=4) +
  geom_smooth(method=lm, se = FALSE)
```

# Fit a linear model with age, state, and interaction as predictors

`cholesterol` as the outcome variable.

```{r}
fit <- lm(cholesterol ~ age * state, data=chol)
summary(fit)
```

# Create an ANOVA table for this fit

```{r}
anova(fit)
```


# Diagnostic plots for full model

```{r}
par(mfrow=c(2, 2))
plot(fit)
```

# Partial F-test for two models


```{r}
fit1 <- lm(cholesterol ~ state, data=chol)
fit2 <- lm(cholesterol ~ state + age, data = chol)
anova(fit1, fit2)
```

# Backwards selection to select the best prediction model

```{r}
library(MASS)
fit <- lm(cholesterol ~ age * state, data=chol)
step <- stepAIC(fit, direction = "backward")
```

AIC = _Akaike's Information Criterion_

